Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-22 paper.qmd
Initial work on removing axes (neglect overlapping)

gen_axes <- function(data, proj_data, proj, limits = 1, axis_pos_x = NULL, axis_pos_y = NULL) {

  rng <- range(proj_data)
  proj_data <- proj_data/max(abs(rng))
  colnames(proj_data) <- c("P1", "P2")
  proj_data <- data.frame(proj_data)
  obs_labels <- as.character(1:nrow(data))

@@

  axis_labels <- colnames(data)
  rownames(axes) <- axis_labels

@@

@@

@@

>>>>

gen_axes <- function(proj, limits = 1, axis_pos_x = NULL, axis_pos_y = NULL, axis_labels) {

@@

  rownames(axes) <- axis_labels

@@

projection_scaled <- projection * 1.23

# projection_filtered <- projection
# projection_filtered[apply(projection_filtered, 1, function(row) all(row < 0)), ] <- 0.75

rows_to_keep <- c(1, 2, 4, 5, 6)

projection_filtered <- projection[rows_to_keep, ]

projected <- as.matrix(scaled_pbmc_data) %*% projection_scaled

@@

projected_model <- as.matrix(scaled_pbmc_data_model) %*% projection_scaled

@@

axes_obj <- gen_axes(
  proj = projection_filtered,
  limits = 1.5,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75,
  axis_labels = paste0("p", rows_to_keep))
